Bayesian Nonparametric System Reliability\\ using Sets of Priors

### 2015-11-20 ijar-npb-ms.tex
improved caption for pdc illu figure

As a simple example, see Figure~\ref{fig:singleprior-pdc} ***

\begin{figure}
\includegraphics[width=\textwidth]{singleprior-pdc}
\caption{Beta densities (left) and corresponding Beta-binomial probability mass functions (right)
for a prior with $\nktz = 8, \yktz = 0.75$,
and posteriors based on $n^k_t=16$ observations with $s^k_t=12$ (Posterior 1) and $s^k_t=0$ (Posterior 2), respectively.
For Posterior 2, the conflict between prior assumptions and data is averaged out;
both posterior density and posterior predictive have the same spread as Posterior 1 for which there is no conflict,
giving a false sense of certainty.}
\label{fig:singleprior-pdc}
\end{figure}

>>>>

As a simple example, see Figure~\ref{fig:singleprior-pdc} ***
giving a false sense of certainty***

\begin{figure}
\includegraphics[width=\textwidth]{singleprior-pdc}
\caption{Beta densities (left) and corresponding Beta-binomial probability mass functions (right)
for a prior with $\nktz = 8, \yktz = 0.75$,
and posteriors based on $n^k_t=16$ observations with $s^k_t=12$ (Posterior~1) and $s^k_t=0$ (Posterior~2), respectively.
Data for Posterior~1 confirm prior assumptions,
while data for Posterior~2 are in conflict with the prior.
However, this conflict is averaged out,
and Posterior 1 and Posterior 2 have the same spread, both in the posterior pdf and the posterior predictive pmf,
such that Posterior 2 gives a false sense of certainty despite the massive conflict between prior and data.}
\label{fig:singleprior-pdc}
\end{figure}
